Figure 6 - networks

### 2024-07-15 ms_figure_6_networks.Rmd
Make Fig 6c narrower

cowplot::plot_grid(
    cowplot::plot_grid(
        cowplot::plot_grid(
            ggr150 + theme(legend.position = "none"), 
            ggr500 + theme(legend.position = "none"), 
            nrow = 1, labels = c("A", "B")
        ),
        get_legend(ggr150 + theme(legend.position = "bottom"), "bottom"),
        nrow = 2, labels = c("", ""), rel_heights = c(1, 0.25)
    ),
    cowplot::plot_grid(
        cowplot::plot_grid(fig6c, ggrad_upset,
                           ncol = 1, labels = c("C", "D"),
                           rel_heights = c(1, 1.25)), 
        pho7volc, 
        nrow = 1, labels = c("", "E")
    ),
    rel_heights = c(5, 3.5), 
    ncol = 1
)
```

>>>>

cowplot::plot_grid(
    cowplot::plot_grid(
        cowplot::plot_grid(
            ggr150 + theme(legend.position = "none"), 
            ggr500 + theme(legend.position = "none"), 
            nrow = 1, labels = c("A", "B")
        ),
        get_legend(ggr150 + theme(legend.position = "bottom"), "bottom"),
        nrow = 2, labels = c("", ""), rel_heights = c(1, 0.25)
    ),
    cowplot::plot_grid(
        cowplot::plot_grid(
            cowplot::plot_grid(NULL, fig6c, NULL, nrow = 1,
                               rel_widths = c(0.25, 1, 0.1)),  
            ggrad_upset,
            ncol = 1, labels = c("C", "D"),
            rel_heights = c(1, 1.75)), 
        pho7volc, 
        nrow = 1, labels = c("", "E")
    ),
    rel_heights = c(5, 3.5), 
    ncol = 1
)
```
